---
title: "hormone-analysis-report"
author: "tmuylder"
date: "11/10/2020"
output: html_document
csl: literature/apa.csl
bibliography: literature/bibliography.bib
---

# Analysis of hormone project

This script analyzes the dataset of the hormone experiment performed on 01/01/2020.
It contains the statistical analysis and plotting of figure 2D of the paper.

Here is a reference to a paper [@Munafo2017].

## 1. Import libraries
Install the packages and load in the libraries:

```{r, warning=FALSE}
#install.packages("ggplot2")
library(ggplot2)
```

## 2. Data analysis

### 2.1 Import samples

Import dataset with proper name handling & rename third column. 

```{r, results='hide'}
hormone <- read.csv2("data/20201102-hormone.csv")
names(hormone)[3] <- "Concentration"
hormone
```


```{r}
summary(hormone)
```

### 2.2 Create figures
Create plot effect of drug A and B on concentration of substance X measured in blood of patients. 

```{r, fig.cap="Result of drug on hormone concentration", fig.width=5, fig.height=2}
ggplot(hormone, aes(Drug,Concentration)) +
  stat_summary(fun=mean, geom="bar") +
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", width=0.25) +  
  geom_point() +
  coord_flip()
```


## 3. Discussion
There is a clear influence of the choice of drugs on the concentration of hormones present in patients blood. 

## 4. Conclusion 

## 5. Final notes
This report was created with R version: `r getRversion()`. The following packages were used for the analysis

```{r}
sessionInfo()
```

## 6. References




